The importance of measurement uncertainty in ecological management

### 2018-01-18 manuscripts/manuscript.Rmd
fix path

sims <- read_csv(file.path(log_dir, "observe_harvest_recruit/sims.csv"), col_types = "inicnnn")
det_sims <- read_csv(file.path(log_dir, "observe_harvest_recruit/det_sims.csv"))
all_policies <- read_csv(file.path(log_dir, "observe_harvest_recruit/all_policies.csv"))
ram_ex <- read_csv(file.path(log_dir, "ram_ex/ram_ex.csv"))

@@

```{r fig.width=7, fig.height=7, fig.cap=""}
priors <- 
  read_csv(file.path(log_dir, "priors.csv")) %>%
  select(states, 
         "POMDP: low prior" = prior_low, 
         "POMDP: high prior" = prior_high) %>%
  gather(prior, belief, -states)

>>>>

sims <- read_csv(file.path(log_dir, "observe_harvest_recruit/sims.csv"), col_types = "inicnnn")
det_sims <- read_csv(file.path(log_dir, "observe_harvest_recruit/det_sims.csv"))
all_policies <- read_csv(file.path(log_dir, "observe_harvest_recruit/all_policies.csv"))
priors <- read_csv(file.path(log_dir, "observe_harvest_recruit/priors.csv"))
ram_ex <- read_csv(file.path(log_dir, "ram_ex/ram_ex.csv"))

@@

```{r fig.width=7, fig.height=7, fig.cap=""}
priors <- 
  priors %>%
  select(states, 
         "POMDP: low prior" = prior_low, 
         "POMDP: high prior" = prior_high) %>%
  gather(prior, belief, -states)
